Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-19 paper.qmd
Fixed Figure 2a

@@

two_curvy_proj_umap_model_benchmark2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df2, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.1, 0.1)) + 
  ylim(c(-0.1, 0.1)) +
  interior_annotation("b2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )
```

@@

two_curvy_proj_umap_model1 + two_curvy_proj_umap_model2 + 
  plot_layout(ncol = 2)
```

>>>>

two_curvy_proj_true <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = true_model_df_proj, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 0.6)) + 
  ylim(c(-0.6, 0.6)) +
  interior_annotation("a", sc_ltr_pos, cex = 1.5) +
  theme(
    legend.position = "none"
  )

@@

two_curvy_proj_umap_model_benchmark2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df2, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.1, 0.1)) + 
  ylim(c(-0.1, 0.1)) +
  interior_annotation("b2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_true2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = true_model_df_proj, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 0.6)) + 
  ylim(c(-0.6, 0.6)) +
  interior_annotation("b", sc_ltr_pos, cex = 1.5) +
  theme(
    legend.position = "none"
  )

@@

two_curvy_proj_true + two_curvy_proj_true2 +
#two_curvy_proj_umap_model1 + two_curvy_proj_umap_model2 + 
  plot_layout(ncol = 2)
```
